---
output:
  md_document:
    variant: gfm
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# stopadforms

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R build status](https://github.com/Sage-Bionetworks/stopadforms/workflows/R-CMD-check/badge.svg)](https://github.com/Sage-Bionetworks/stopadforms/actions)
<!-- badges: end -->

stopadforms is an R package and Shiny application to allow reviewers to view and
score submissions to the [STOP-AD Compound Submission Portal](https://stopadportal.synapse.org/#/).

The application is hosted at https://shinypro.synapse.org/users/kwoo/stopadforms/.
To use it, you must be a member of the
[STOP-AD_Reviewers Synapse team](https://www.synapse.org/#!Team:3403721) 
and be logged in to Synapse. To save reviews, you must be a Certified User on
Synapse.

## Installation

```{r install, eval = FALSE}
devtools::install_github("Sage-Bionetworks/stopadforms")
```

## Running the application locally

```{r show-app, eval = FALSE}
library("stopadforms")
run_app()
```

See `vignette("deploying-stopadforms", package = "stopadforms")` for information
on how we deploy the app on the Sage Bionetworks Shiny Pro server.

---

Please note that the stopadforms project is released with a [Contributor Code of
Conduct](.github/CODE_OF_CONDUCT.md). By contributing to this project, you agree
to abide by its terms.
