---
output:
  md_document:
    variant: gfm
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# stopadforms

<!-- badges: start -->
[![R build status](https://github.com/Sage-Bionetworks/stopadforms/workflows/R-CMD-check/badge.svg)](https://github.com/Sage-Bionetworks/stopadforms/actions)
<!-- badges: end -->

stopadforms is an R package and Shiny application to allow reviewers to view and
score submissions to the [STOP-AD Compound Submission Portal](https://stopadportal.synapse.org/#/).

The application is hosted at https://shinypro.synapse.org/users/kwoo/stopadforms/.
To use it, you must be a member of the
[STOP-AD_Reviewers Synapse team](https://www.synapse.org/#!Team:3403721) 
and be logged in to Synapse. To save reviews, you must be a Certified User on
Synapse.

## Installation

```{r install, eval = FALSE}
devtools::install_github("Sage-Bionetworks/stopadforms")
```

## Running the application locally

```{r show-app, eval = FALSE}
library("stopadforms")
run_app()
```

See `vignette("deploying-stopadforms", package = "stopadforms")` for information
on how we deploy the app on the Sage Bionetworks Shiny Pro server.

## Example: calculating scores for a submission

```{r score, eval = FALSE}
library("synapseforms")
library("reticulate")
library("tidyverse")
library("stopadforms")

# Optional: use reticulate::use_python() here to set path to Python version you want
# to use
synapse <- import("synapseclient")
syn <- synapse$Synapse()
syn$login() # Authenticate to Synapse

## Get rejected submissions (rejected submissions include a test submission I
## created) -- in order to run this you will need to be part of the
## STOP-AD_Reviewers team on Synapse (https://www.synapse.org/#!Team:3403721)
sub_data_files <- get_submissions(
  syn,
  group = 9,
  statuses = "REJECTED"
)

## Convert to data frame
dat_full <- process_submissions(
  sub_data_files,
  lookup_table = stopadforms:::lookup_table,
  complete = TRUE
)

## Filter to one submission of interest -- a test submission I created.
dat <- filter(dat_full, form_data_id == "242")

## Append clinical modifier used in calculations
submission <- append_clinical_to_submission(dat)

## Get section scores
scores <- pull_reviews_table(syn, "syn22014561", submission)

## Calculate overall score
calculate_submission_score(submission, scores)
```

---

Please note that the stopadforms project is released with a [Contributor Code of
Conduct](.github/CODE_OF_CONDUCT.md). By contributing to this project, you agree
to abide by its terms.
